Towards the near-infrared detection of brown dwarf companions: Exploring methods to detect low mass stellar companions from blended spectra \thanks{Based on observations collected at the European Organisation for Astronomical Research in the Southern Hemisphere under ESO programme 089.C-0977(A)}

### 2018-07-30 nir_companions.tex
Work on comments more.

% Abstract of the paper
\begin{abstract}
    {\rd A}We perform an exploratory study on how to directly detect the near-infrared spectrum of candidate brown dwarf (BD) companions around FGK stars to measure or constrain their masses, thereby asserting their stellar nature or discarding it. {\rd B}We explore two different methods to probe the faint spectra of BD companions. The first technique involves the direct subtraction of two observations shifted to mutually cancel out the spectra of the host star. The second technique applies a \(\chi^{2}\) fit to the individual observations with a synthetic binary model comprised of two PHOENIX-ACES spectra, representing the spectra from the host and companion. The observed spectra are wavelength calibrated and corrected for the atmospheric absorption with the aid of synthetic telluric models.
    {\rd C}The direct subtraction method failed to detect the signature of the companions. The \(\chi^{2}\) technique developed here is able to fit the component for the host star but unable to successfully detect the faint spectra of even the largest companion in our sample. We explore how the companion recovery performs on simulated observations and discuss reasons for the non-detection observed. From the synthetic spectra we determine the upper mass limit for the companions to be around \(\rm 600^{+20}_{-40}~M_{Jup}\) as the limitation of this technique for the data we had on hand. {\rd D}This work highlights the challenges in the spectral detection of faint BD companions. We explore the limitations of the direct subtraction method in the case of small RV separation, and attempt companion recovery at low companion/host flux ratios below 3\%, finding a high upper mass limit from the technique. {\rd This is a simple template for authors to write new MNRAS papers.
The abstract should briefly describe the aims, methods, and main results of the paper.
It should be a single paragraph not more than 250 words (200 words for Letters).
No references should appear in the abstract.}
\end{abstract}

@@

\section{Motivation and target selection}
\label{sec:motivation}
The work of~\citet{sahlmann_search_2011} identified several candidate brown dwarf companions of FGK stars with \(\rm M_2 \sin{i}\) values >\(\rm 10~M_{Jup}\). Seven candidates {\rd from~\citet{sahlmann_search_2011}} were selected for {\rd further} observation in order to identify their stellar nature. The target host stars are presented in Table~\ref{tab:starparams} with their stellar parameters, while the companion orbital parameters are provided in Table~\ref{tab:orbitparams}.

@@

We note that there are many variations on this wavelength-calibration technique including those integrated within programs such as TelFit~\citet{gullikson_correcting_2014}, and ESOs Molecfit~\citet{smette_molecfit_2015}, that perform telluric correction and re-calibrate the wavelength axis themselves. {\rd Including concurrent fitting of a stellar spectral model, adjusted for RV, along with the telluric model such as done in other recent works \citep[e.g.][]{}\textbf{Add extra papers here} could help to improve the wavelength calibration preformed here. For example \citet{piskorz_evidence_2016} use only a telluric line model at other near-infrared wavelengths but include a stellar model specifically around 2\,$\mu$m where the telluric lines are weaker.}

@@

@@

The observations were gathered having in mind the application of a differential subtraction method~\citep[e.g.][]{ferluga_separating_1997, kostogryz_spectral_2013} to detect the spectra of the faint BD companions. In short, we Doppler shift each observation to the rest frame of the host star and then mutually subtract the spectra from pairs of observations to cancel out the spectra of the brighter host star. The residuals from this method should contain two copies of the faint companion, subtracted from each other with a radial velocity offset \(\Delta RV\), one positive and one negative. This RV offset, if detectable, would allow the mass ratio to be determined and hence the companion mass.

Due to the poorly separated observation times relative to the long orbital periods, this method was revealed to be inappropriate for these observations as the RV separation of the companion spectra between observations (\(\le 2.3\)\kmps{}) is significantly smaller than the FWHM (full width half maximum) of individual spectral lines (\(\sim\)6\kmps at \(\rm R=50\,000\)).  The small separation of the companion causes the lines of the companion to also mutually cancel, severely reducing the residual signal to well below the available noise level. The requirement of well separated RVs for the companion spectra was clearly stated in the original proposal but was not satisfied when the observations were obtained\footnote{see Sect.~\ref{subsubsec:differential scedualing} for more details}. Radial velocity constraints are also valid for other studies such as the detection of reflected light from exoplanets~\cite{martins_evidence_2015}. The largest estimated companion \(\Delta RV\) separation between the observations of each target is provided in the {\rd \textbf{fifth}} column of Table~\ref{tab:estimatedparameters}.

@@

\section{Binary synthetic spectral recovery}
\label{subsec:companion_recovery}
Since the differential method is ineffective for our dataset due to the RV separation between observations, we explored a second approach to detect the presence of the faint companion spectra. This second approach compares the observed spectra to combinations of synthetic spectral models using \(\chi^{2}\) methods which have been extensively used in the literature~\citep[e.g.][]{astudillo-defru_harps_2015, passegger_fundamental_2016, zechmeister_spectrum_2018,nemravova_xtauri_2016}.

@@

\subsection{\texorpdfstring{\(\chi^{2}\)} method}
\label{subsec:chi2}
The well known \(\chi^{2} \) technique measures the weighted sum of the squared deviation between the observation (\({O}_{i}\)) and the computed models (\(C_{i}\)), with the minimum \(\chi^2\) value representing the best-fit parameters.
\[\chi^{2} = {\Sigma}_i { (O_{i} - C_{i})}^2 / {\sigma}_{i}, \] where \({\sigma}_{i}\) is the error on each measurement. We estimate the \(\sigma\) of each spectrum using the \(\beta\sigma\) method~\citep{czesla_posteriori_2018}, using the MAD (median absolute deviation about the median) robust estimator, an order of approximation of 5, and a jump parameter of 2. We apply the same \(\sigma\) value to all points \({\sigma}_{i} = \sigma\). The \(\beta\sigma\) method provided \(\sigma\) estimates for the target spectra which correspond inversely to signal-to-noise ratios between 100--500.

@@

\subsubsection{Single component model}
\label{subsubsec:single-model}
The single model \(C^{1}_{i}\) comprises of a single synthetic spectrum, \(J\), (with model parameters \(T_{\textrm{eff}}\), logg, [Fe/H]) and is Doppler shifted by a RV value \({rv}_1\).

@@

\subsubsection{Effective radius}
\label{subsection-radius}

@@

\subsection{Reducing parameters}
\label{subsec:reduce-params}
The high dimensionality of the binary model makes it computationally challenging and difficult to analyze the \(\chi^2\) space. 
For reference, the available parameter space is squared when increasing from one spectral component in the single model to a binary model, and therefore becomes computationally expensive. In general the number of possible parameter combinations for \(c\) spectral components each with a grid of \(m\) models increases to \(c^m\). If the full set of PHOENIX-ACES library spectra (66456) is explored with a binary fit then this naively balloons to over 4.4 billion possible combinations. Half of these are not unique as the host and companion components are swapped. This is the worst case scenario and we implement a number of assumptions to vastly reduce the parameter-space enabling faster computation.

Our first assumption is to restrict ourselves to models with an Alpha element abundance (\([\alpha\)/Fe]) of zero. This is likely a very good approximation as all our targets have solar metallicity and are thus very likely to belong to the thin disk of the Galaxy, where \([\alpha\)/Fe] values are close to zero (i.e., solar) -- e.g.~\citet{adibekyan_chemical_2012}. Our second is to assume that we can significantly reduce the search space with literature values for the host star. We fix the metallicity of both components to the closest grid to the literature value (usually [Fe/H] =0.00). We also fix the logg of the host star to its literature values given in Table~\ref{tab:starparams}. The uncertainties on the literature measurements for logg (\(\sim\)0.1) and metallicity (\(\sim\)0.05) are both smaller than the grid steps of 0.5 for these parameters.
For the logg of the companion we use the~\citet{baraffe_evolutionary_2003,baraffe_new_2015} evolutionary model value for the given companions \(\textrm{M}_2\)/\(\textrm{M}_2\sin{i}\) and hosts age.

@@

@@

The results of two example binary simulations are displayed in Figs.~\ref{fig:Mdwarf_contours} and ~\ref{fig:HD211847_simulated_contours},both simulated with a SNR of 150. The input and recovered parameters for the binary components are indicated by the red circles and yellow stars respectively, and are given in Table~\ref{tab:example_params}. 
The 3-\(\sigma\) contour is shown in white on the plots to indicate the shape of the confidence level only. The 1-\(\sigma\) contours are not shown here as they are much smaller than the temperature grid step and are not easy to visualize at this scale as they are often smaller than the marker shown at the minimum location. Each colored rectangle is centered on the grid point, with its shape indicating the resolution of the grid space searched.

@@

\begin{figure*}
    \centering
    \includegraphics[width=\hsize]{images/Mdwarf_pcolors.pdf}

    \caption{\(\chi^2\) results for companion recovery of a simulated binary observation of a Sun-like star (\(T_{\textrm{eff}_1}=5800\)~K) with an M-dwarf companion (\(T_{\textrm{eff}_2}=4000\)~K). The top right plot shows the application of a single component model (\(C^1\)) while the other three are using a binary model (\(C^2\)). Both left hand panels show the distribution of host temperature and host RV. The top right panel shows the distribution for host and companion temperature, and the bottom right the companion temperature and radial velocity.
        The red circle and yellow star indicate the location of the simulation input and recovered parameters respectively.
        The white line shows a 3-\(\sigma\) confidence level about the minimum \(\chi^2\) solution grid point. Each box is centered on the parameter values and shows the grid resolution.}
    \label{fig:Mdwarf_contours}
\end{figure*}

\begin{figure*}
    \centering
    \includegraphics[width=\hsize]{images/HD211847_example_pcolors.pdf}
    \caption{Similar to Fig.~\ref{fig:Mdwarf_contours}, \(\chi^2\) results for companion recovery of a simulated binary observation similar to {HD 211847}, (\(T_{\textrm{eff}_1} = 5800\)~K, \(T_{\textrm{eff}_2}=3200\)~K). The top right plot shows the application of a single component model (\(C^1\)) while the other three are using a binary model (\(C^2\)). Both left hand panels show the distribution of host temperature and host RV. The top right panel shows the distribution for host and companion temperature, and the bottom right the companion temperature and radial velocity.
        The red circle and yellow star indicate the location of the simulation input and recovered parameters respectively.
        The white line shows a 3-\(\sigma\) confidence level about the minimum \(\chi^2\) solution grid point. Each box is centered on the parameter values and shows the grid resolution.}
    \label{fig:HD211847_simulated_contours}
\end{figure*}

\subsection{HD211847 observation}
\label{subsection:results-hd211847}
{HD 211847} is the best candidate for detection as it has a \(\rm 155~M_J\) low-mass star companion~\citet{moutou_eccentricity_2017}. Even though it is not a BD it has the highest estimated flux ratio, of 0.03. The result of applying \(\chi^2\) fitting to the second observation of {HD 211847} is shown in Fig.~\ref{fig:HD211847_result_contours}.

@@

\begin{figure*}
    \centering
    \includegraphics[width=\linewidth]{images/HD211847_result_pcolors.pdf}
    \caption{\(\chi^2\) result grid for observation 2 of {HD 211847}, similar to Figs.~\ref{fig:Mdwarf_contours} and~\ref{fig:HD211847_simulated_contours}. The top right plot shows the application of a single component model (\(C^1\)) while the other three are using a binary model (\(C^2\)). Both left hand panels show the distribution of host temperature and host RV. The top right panel shows the distribution for host and companion temperature, and the bottom right the companion temperature and radial velocity. The red circles indicate the literature values or calculated parameters for the target while the yellow star indicates the minimum \(\chi^2\) solution. The error bar on the \(T_{\textrm{eff}_1}\) is from the literature while the error bars on \({rv}_1\) and \({rv}_2\) are calculated by propagating the orbital parameter uncertainties though the radial velocity equation. The white line shows a 3-\(\sigma\) confidence level about the minimum \(\chi^2\) solution grid point, not always visible here due to the large \(\chi^2\) values.}
    \label{fig:HD211847_result_contours}
\end{figure*}

@@

@@

\begin{figure}
    \centering
    \includegraphics[width=\hsize]{images/inject_recovery_hd30501.pdf}
    \caption{Result of simulated injection-recovery of synthetic companions on {HD 30501}. The blue dots and orange triangles indicate the recovered companion temperature with \(\pm100\)~K error bars for observed and synthetic spectra respectively. The black dashed diagonal shows the 1:1 temperature relation. The grey shaded region indicates the \(\pm1000\)~K temperature range explored. Gaussian noise added to the synthetic spectra was derived from the observed spectra.}
    \label{fig:injection-recovery}
\end{figure}

@@

\section{Discussion}
\label{sec:discussion}
The spectral differential and the synthetic recovery methods attempted here were both unsuccessful in a detection of the BD companion spectra.  The upper mass limits of \(600^{+20}_{-40} \) we set for these companions is very high, roughly six times higher then the BD mass limit \(\rm\sim 80-90~M_{Jup}\).
We discuss potential reasons and solutions for these poor results below, list the lessons learned in this exploratory study, and provide some guidance for any future attempts with these methods.

>>>>

% Abstract of the paper
\begin{abstract}
    {\rd A}We perform an exploratory study on how to directly detect the near-infrared spectrum of candidate brown dwarf (BD) companions around FGK stars to measure or constrain their masses, thereby asserting their stellar nature or discarding it. {\rd B}We explore two different methods to probe the faint spectra of BD companions. The first technique involves the direct subtraction of two observations shifted to mutually cancel out the spectra of the host star. The second technique applies a \(\chi^{2}\) fit to the individual observations with a synthetic binary model comprised of two PHOENIX-ACES spectra, representing the spectra from the host and companion. The observed spectra are wavelength calibrated and corrected for the atmospheric absorption with the aid of synthetic telluric models.
    {\rd C}The direct subtraction method failed to detect the signature of the companions. The \(\chi^{2}\) technique developed here is able to fit the component for the host star but unable to successfully detect the faint spectra of even the largest companion in our sample. We explore how the companion recovery performs on simulated observations and discuss reasons for the non-detection observed. {\rd From the injection-recovery analysis this technique in, its current form, is insufficient below 3800~K which corresponds to an upper mass limit for the companions to be around \(\rm 600^{+20}_{-40}~M_{Jup}\)}. {\rd D}This work highlights the challenges in the spectral detection of faint BD companions. We explore the limitations of the direct subtraction method in the case of small RV separation, and attempt companion recovery at low companion/host flux ratios below 3\%, finding a high upper mass limit from the technique. {\rd This is a simple template for authors to write new MNRAS papers.
The abstract should briefly describe the aims, methods, and main results of the paper.
It should be a single paragraph not more than 250 words (200 words for Letters).
No references should appear in the abstract.}
\end{abstract}

@@

\section{Motivation and target selection}
\label{sec:motivation}
The work of~\citet{sahlmann_search_2011} identified several candidate brown dwarf companions of FGK stars with \(\rm M_2 \sin{i}\) values >\(\rm 10~M_{Jup}\). Seven candidates {\rd from~\citet{sahlmann_search_2011}}, which were visible in Period 89,  were selected for {\rd further} observation in order to identify their stellar nature. The target host stars are presented in Table~\ref{tab:starparams} with their stellar parameters, while the companion orbital parameters are provided in Table~\ref{tab:orbitparams}.

@@

We note that there are many variations on this wavelength-calibration technique including those integrated within programs such as \emph{TelFit}~\citet{gullikson_correcting_2014}, and ESOs \emph{Molecfit}~\citet{smette_molecfit_2015}, that perform telluric correction and re-calibrate the wavelength axis themselves. {\rd Including concurrent fitting of a stellar spectral model, adjusted for RV, along with the telluric model such as done in other recent works \citep[e.g.][]{}\textbf{Add extra papers here} could help to improve the wavelength calibration preformed here. For example \citet{piskorz_evidence_2016} use only a telluric line model at other near-infrared wavelengths but include a stellar model specifically around 2\,$\mu$m where the telluric lines are weaker.}

@@

{\rd  The recent work of \citet{piskorz_evidence_2016} use a PCA technique to correct for the telluric spectra by applying it to several (number not specified) AB nodding pairs over their 60-180 minute integration time. We are uncertain if this technique would work as effectively on our observations due to our shorter integration time (24 minutes) would have less telluric variation present across the 8 nod spectra . A recent comparison of three telluric correction methods, \emph{Molecfit} and {TelFit} and {TAPAS} to the standard star method by \cite[][in prep.]{ulmer-mol _2018} found that all three synthetic models preform better at correcting for atmospheric H$_2$O compared to the standard star method with \emph{Molecfit}, being a more complete tool, preforming slightly better over TAPAS.}

@@

The observations were gathered having in mind the application of a differential subtraction method~\citep[e.g.][]{ferluga_separating_1997, kostogryz_spectral_2013} to detect the spectra of the faint BD companions. In short, we Doppler shift each observation to the rest frame of the host star and then mutually subtract the spectra from pairs of observations to cancel out the spectra of the brighter host star. The residuals from this method should contain two copies of the faint companion, subtracted from each other with a radial velocity offset \(\Delta RV\) between them. This RV offset, if detectable, would allow the mass ratio to be determined and hence the companion mass.

Due to the poorly separated observation times relative to the long orbital periods, this method was revealed to be inappropriate for these observations as the RV separation of the companion spectra between observations (\(\le 2.3\)\kmps{}) is significantly smaller than the FWHM (full width half maximum) of individual spectral lines (\(\sim\)6\kmps at \(\rm R=50\,000\)).  The small separation of the companion causes the lines of the companion to also mutually cancel, severely reducing the residual signal to well below the available noise level. The requirement of well separated RVs for the companion spectra was clearly stated in the original proposal but was not satisfied when the observations were obtained\footnote{see Sect.~\ref{subsubsec:differential scedualing} for more details}. {\rd The very large orbital periods of some of the targets would not produce a sufficient RV signal during one semester. This was a possible oversight during the proposal stage.} The largest estimated companion \(\Delta RV\) separation between the observations of each target is provided in the seventh column of Table~\ref{tab:estimatedparameters}. Radial velocity constraints are also valid for other studies such as the detection of reflected light from exoplanets~\cite{martins_evidence_2015}.

@@

\section{Binary synthetic spectral recovery}
\label{subsec:companion_recovery}
Since the differential method is ineffective for our dataset due to the RV separation between observations, we explored a second approach to detect the presence of the faint companion spectra. This second approach compares the observed spectra to combinations of synthetic spectral models using \(\chi^{2}\) methods which have been extensively used in the literature~\citep[e.g.][]{astudillo-defru_harps_2015, passegger_fundamental_2016, zechmeister_spectrum_2018,nemravova_xtauri_2016}. {\rd The temperature of synthetic spectra fitted to  the companion will provide some indication of the companions spectral type, but will not produce a direct mass constraint that was the original aim of this work.}

@@

\subsection{\texorpdfstring{\(\chi^{2}\)}\ \ method}
\label{subsec:chi2}
The well known \(\chi^{2} \) technique measures the weighted sum of the squared deviation between the observation (\({O}_{i}\)) and the computed models (\(C_{i}\)), with the minimum \(\chi^2\) value representing the best-fit parameters.
\[\chi^{2} = {\Sigma}_i { (O_{i} - C_{i})}^2 / {\sigma}_{i}, \] where \({\sigma}_{i}\) is the error on each measurement. We estimate the \(\sigma\) of each spectrum using the \(\beta\sigma\) method~\citep{czesla_posteriori_2018}, using the MAD (median absolute deviation about the median) robust estimator. {\rd This method estimates the spectral noise using numerical derivatives of the spectra. We followed the procedure outlined in \citet{czesla_posteriori_2018}, analysing the results from successive parameter combinations to settle on an order of approximation (derivative level) of 5, and a jump parameter (pixels skipped to avoid correlations) of 2.} We apply the same \(\sigma\) value to all points \({\sigma}_{i} = \sigma\). The \(\beta\sigma\) method provided \(\sigma\) estimates for the target spectra which correspond inversely to signal-to-noise ratios between 100--500, {\rd similar to the values given in Table~\ref{tab:observations} calculated from the continuum of detector 2.}

@@

\subsubsection{Single component model}
\label{subsubsec:single-model}
The single model \(C^{1}_{i}\) comprises of a single synthetic spectrum, \(J\), (with model parameters \(T_{\textrm{eff}}\), logg, [Fe/H], ([\(\alpha\)/Fe]) and is Doppler shifted by a RV value \({rv}_1\).

@@

{\rd The full list of grid parameters for the binary model are \(T_{\textrm{eff}}1\),  \(\rm logg_1\), [Fe/H]$_1$, [\(\alpha\)/Fe]$_1$, ${rv}_1$, \(T_{\textrm{eff}}2\), \(\rm logg_2\), [Fe/H]$_2$, [\(\alpha\)/Fe]$_2$, ${rv}_2$ where the subscripts 1 and 2 indicate the host and companion models respectively.}
\subsubsection{Effective radius}
\label{subsection-radius}

@@

\subsection{Reducing parameters}
\label{subsec:reduce-params}
The high dimensionality of the binary model makes it computationally challenging and difficult to analyze the \(\chi^2\) space. 
For reference, the multiplicative parameter space is squared when increasing from one spectral component in the single model to a binary model, and therefore becomes computationally expensive. In general the number of possible parameter combinations for \(c\) spectral components each with a grid of \(m\) models increases to \(c^m\). If the full set of PHOENIX-ACES library spectra (66456) is explored with a binary fit then this naively balloons to over 4.4 billion possible combinations. Half of these are not unique as the host and companion components are swapped. This is the worst case scenario and we implement a number of assumptions to vastly reduce the parameter-space enabling faster computation.

Our first assumption is to restrict ourselves to models with an Alpha element abundance ([\(\alpha\)/Fe]) of zero. This is likely a very good approximation as all our targets have solar metallicity and are thus very likely to belong to the thin disk of the Galaxy, where [\(\alpha\)/Fe] values are close to zero (i.e., solar) -- e.g.~\citet{adibekyan_chemical_2012}. Our second is to assume that we can significantly reduce the search space with literature values for the host star. We fix the metallicity of both components to the closest grid to the literature value (usually [Fe/H] =0.00). We also fix the logg of the host star to its literature values given in Table~\ref{tab:starparams}. The uncertainties on the literature measurements for logg (\(\sim\)0.1) and metallicity (\(\sim\)0.05) are both smaller than the grid steps of 0.5 for these parameters.
For the logg of the companion we use the~\citet{baraffe_evolutionary_2003,baraffe_new_2015} evolutionary model value for the given companions \(\textrm{M}_2\)/\(\textrm{M}_2\sin{i}\) and hosts age.

@@

For the companions targets with fully resolved orbits the known RV of  the host star, \({rv}_1\) could also have been fixed. We however left this free to see if the known value would be recovered by the fitting.

@@

The results of two example binary simulations are displayed in Figs.~\ref{fig:Mdwarf_contours} and ~\ref{fig:HD211847_simulated_contours}, both simulated with a SNR of 150. The input and recovered parameters for the binary components are indicated by the red circles and yellow stars respectively, and are given in Table~\ref{tab:example_params}. 
The 3-\(\sigma\) contour is shown in white on the plots to indicate the shape of the confidence level only. The 1-\(\sigma\) contours are not shown here as they are much smaller than the temperature grid step and are not easy to visualize at this scale as they are often smaller than the marker shown at the minimum location. Each colored rectangle is centered on the grid point, with its shape indicating the resolution of the grid space searched.

@@

\begin{figure*}
    \centering
    \includegraphics[width=0.8\hsize]{images/Mdwarf_pcolors.pdf}

    \caption{\(\chi^2\) results for companion recovery of a simulated binary observation of a Sun-like star (\(T_{\textrm{eff}_1}=5800\)~K) with an M-dwarf companion (\(T_{\textrm{eff}_2}=4000\)~K). The top right plot shows the application of a single component model (\(C^1\)) while the other three are using a binary model (\(C^2\)). Both left hand panels show the distribution of host temperature and host RV. The top right panel shows the distribution for host and companion temperature, and the bottom right the companion temperature and radial velocity.
        The red circle and yellow star indicate the location of the simulation input and recovered parameters respectively.
        The white line shows a 3-\(\sigma\) confidence level about the minimum \(\chi^2\) solution grid point. Each box is centred on the parameter values and shows the grid resolution.}
    \label{fig:Mdwarf_contours}
\end{figure*}

\begin{figure*}
    \centering
    \includegraphics[width=0.8\hsize]{images/HD211847_example_pcolors.pdf}
    \caption{Similar to Fig.~\ref{fig:Mdwarf_contours}, \(\chi^2\) results for companion recovery of a simulated binary observation similar to {HD 211847}, (\(T_{\textrm{eff}_1} = 5800\)~K, \(T_{\textrm{eff}_2}=3200\)~K). The top right plot shows the application of a single component model (\(C^1\)) while the other three are using a binary model (\(C^2\)). Both left hand panels show the distribution of host temperature and host RV. The top right panel shows the distribution for host and companion temperature, and the bottom right the companion temperature and radial velocity.
        The red circle and yellow star indicate the location of the simulation input and recovered parameters respectively.
        The white line shows a 3-\(\sigma\) confidence level about the minimum \(\chi^2\) solution grid point. Each box is centered on the parameter values and shows the grid resolution.}
    \label{fig:HD211847_simulated_contours}
\end{figure*}

\subsection{HD211847 observation}
\label{subsection:results-hd211847}
{HD 211847} is the best candidate for detection as it has a \(\rm 155~M_J\) low-mass star companion~\citet{moutou_eccentricity_2017}. The angular separation of the two bodies is 222 mas (or 11.3 au). Even though it is not a BD it has the highest estimated flux ratio in our sample, of 0.03 based on the \citet{baraffe_new_2015} evolution models and the known companion mass (see. Table~\ref{tab:estimatedparameters}). The angular separation of HD211847B is 222 mas with a projected distance of The result of applying \(\chi^2\) fitting to the second observation of {HD 211847} is shown in Fig.~\ref{fig:HD211847_result_contours}.

@@

\begin{figure*}
    \centering
    \includegraphics[width=0.8\linewidth]{images/HD211847_result_pcolors.pdf}
    \caption{\(\chi^2\) result grid for observation 2 of {HD 211847}, similar to Figs.~\ref{fig:Mdwarf_contours} and~\ref{fig:HD211847_simulated_contours}. The top right plot shows the application of a single component model (\(C^1\)) while the other three are using a binary model (\(C^2\)). Both left hand panels show the distribution of host temperature and host RV. The top right panel shows the distribution for host and companion temperature, and the bottom right the companion temperature and radial velocity. The red circles indicate the literature values or calculated parameters for the target while the yellow star indicates the minimum \(\chi^2\) solution. The error bar on the \(T_{\textrm{eff}_1}\) is from the literature while the error bars on \({rv}_1\) and \({rv}_2\) are calculated by propagating the orbital parameter uncertainties though the radial velocity equation. The white line shows a 3-\(\sigma\) confidence level about the minimum \(\chi^2\) solution grid point, not always visible here due to the large \(\chi^2\) values.}
    \label{fig:HD211847_result_contours}
\end{figure*}

@@

{\rd BIC FOR HD211847###########}

@@

\begin{figure}
    \centering
    \includegraphics[width=\hsize]{images/inject_recovery_hd30501.pdf}
    \caption{Result of simulated injection-recovery of synthetic companions on {HD 30501}. The blue dots and orange triangles indicate the recovered companion temperature for the observed and synthetic spectra respectively. The \(\pm100\)~K error bars are the grid step of the synthetic models. The black dashed diagonal shows the 1:1 temperature relation. The grey shaded region indicates the \(\pm1000\)~K temperature range explored. Gaussian noise added to the synthetic spectra was derived from the observed spectra.}
    \label{fig:injection-recovery}
\end{figure}

@@

\section{Discussion}
\label{sec:discussion}
The spectral differential and the synthetic recovery methods attempted here were both unsuccessful in a detection of the BD companion spectra.  The upper mass limits of \(600^{+20}_{-40} \) we set for these companions is very high, roughly six times higher then the BD mass limit \(\rm\sim 80-90~M_{Jup}\).
We discuss potential reasons and solutions for these poor results below, list the lessons learned in this exploratory study, and provide some guidance for any future attempts with these methods. {\rd We do note that there have been recent works, that have had successful detection of non-transiting giant planets, they use a different technique cross correlation and maximum likelyhood....} They are successful due to spectra with much higher SNR, longer wavelength range.    XXXXXXXXXXXXXXXXXXXXXXX
